---
title: "[Unilur](https://github.com/ginolhac/unilur) Example"
format: 
  unilur-html: default
  unilur-html+solution:
    output-file: example-solution.html
  unilur-pdf: default
  unilur-pdf+solution:
    output-file: example-solution.pdf
embed-resources: true
---

```{r}
#| include: false
library(reticulate) # for the python example
```


## Usage once extension is installed

- **Activate** the extension by adding the following lines to your YAML header:

``` yaml
format:
  unilur-html: default
  unilur-html+solution:
    # You have to specify a different output file otherwise they will 
    # overwrite themselves
    output-file: example-solution.html 
```

When you call `quarto render`, two HTML files will be produced. The one named
`example-solution.html` will have the solution blocks included.

- **Solution** code blocks are **highlighted** or ~~discarded~~ according to the chunk option `unilur-solution` Boolean and the global option `show-solution` in the YAML header.

Of note, if `show-solution` is absent, it is considered `false`.


### Example with `unilur-solution: true`

- Code chunk with `echo: fenced`

```{r}
#| unilur-solution: true
#| echo: fenced

1 + 1
```

- Code block _without_ solution, so stays in whatever happens

```{r}
#| echo: fenced

1 + 1
```

- Solution with `unilur-collapse: false` 

```{r}
#| unilur-solution: true
#| unilur-collapse: false

1 + 2
```


Any machinery supported by Quarto can be used:

- Python Code chunk with `unilur-solution: true`

```{python}
#| unilur-solution: true
for i in [3, 5, 6]:
  print(i)
```


::: {.callout-caution}
## Danger
Red expected
:::

- Solution with markdown text (`{block}`):

````{block}
#| unilur-solution: true
#| unilur-collapse: false
For text with **bold** or warning people about CO~2~ atmospheric concentration

R code can be displayed but not executed.

```{{r}}

1 + 1
```

````

You can also include `div` labels with `unilur-solution`. 
Note the solution will only show up in the solution file.

::: unilur-solution

Here is a solution that is inside a div. The contents of this will only be shown
in the solution document. Source code highlighting is preserved inside the `div` and executable.

```{r}

sample(CO2,  size = 5) |> 
  head(5)

```

:::

The advantage of working inside the div labels is that standard code formatting and
highlighting will apply, and code can be executed alongside standard text.
