---
title: "Practical collapse"
subtitle: "global option"
author: "A Ginolhac"
date: "2025-09-22"
format: unilur-html
show-solution: true
collapse-solution: false
embed-resources: true
---

::: {.callout-note}
This practical has:

- `show-solution: true`, solution are displayed.
- `collapse-solution: false`, solution are **not** collapsed (collapsed is the usual default mode)
:::


##### Generate 5 numbers from the uniform distribution between 0 and 1

```{r}
#| unilur-solution: true

runif(n = 5)
```

The next solution collapsed despite the global option because of its specific option: `#| unilur-collapse: true`

##### Generate 5 numbers from the uniform distribution between 5 and 10

```{r}
#| unilur-solution: true
#| unilur-collapse: true

 runif(n = 5, min = 5, max = 10)
```


##### Generate 5 numbers from the strandard distribution

```{r}
#| unilur-solution: true

 rnorm(n = 5)
```

Next block is also collapsed individually

##### Results are always changing, how to get identical random numbers?

```{block}
#| unilur-solution: true
#| unilur-collapse: true

Use the `set.seed(xx)` where `xx` is a fixed number.
```
